---
title: "Other Responses"
date: "10/14/2021"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: journal
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r include = FALSE}
knitr::opts_chunk$set(echo=FALSE, warning = FALSE)
library(gt)
library(fs)
library(purrr)
library(tidyverse)
theme_set(theme_minimal(15))
```

```{r setup, include=FALSE}
converting_read <- function(curr_path){
  print(curr_path)
  read_csv(curr_path) %>% mutate(sub = as.character(sub),
                                 resp_obj = as.character(resp_obj))
}

converting_read2 <- function(curr_path){
  print(curr_path)
  read_csv(curr_path) %>% mutate(sub = as.character(sub),
                                 post_first_resp_obj = as.character(post_first_resp_obj))
}

# Loading behavioral data
sub_dir = dir_ls("../Monstera/data")
prescan_behav <- map(sub_dir, dir_ls, glob = '*prescan*_behav*.csv') %>% unlist()
scan_behav <- map(sub_dir, dir_ls, regexp = '(.*)_scan\\d_behav_.*') %>% unlist()

prescan_batch <- map_dfr(prescan_behav, converting_read)
scan_batch <- map_dfr(scan_behav, converting_read2)

```


# Scan Phase 

Subjects who answered at least 3 times during the route 

*i_pic = image selected at first response* 

*n_other_res = number of responses made during the route excluding the first response* 

```{r}
multiple = scan_batch %>% filter(other_resp != "[-999]") %>% mutate(correct = ifelse(post_first_resp_obj == destination, 1, 0)) 
v = strsplit(multiple$other_resp, " ")

numOfTimes = 1
for (i in 2:length(v)) {
  n = length(v[[i]]) / 3
  numOfTimes <- c(numOfTimes, n)
}

multiple %>% mutate(n_other_res = numOfTimes) %>% select(sub, i_pic, n_other_res, correct) %>% filter(n_other_res != 1) %>% group_by(sub) %>% arrange(desc(n_other_res)) %>% gt()

```

```{r include = FALSE}

```


2)

Top 6 subjects who responded more than once during the route while the first response was not at image 1

*n = number of trials* 

```{r}
scan_batch %>% filter(other_resp != "[-999]" & i_pic != 1) %>% group_by(sub) %>% summarise(n=n()) %>% arrange(desc(n)) %>% head() %>% gt()
```


Top 6 subjects who responded more than once during the route (first response at image 1 included)

```{r}
scan_batch %>% filter(other_resp != "[-999]") %>% group_by(sub) %>% summarise(n=n()) %>% arrange(desc(n)) %>% head() %>% gt()

```


3)

Subjects with first response during the same segment, but not at image 1 

```{r}

press_twice = scan_batch %>% 
  filter(other_resp != "[-999]" & i_pic != 1 & i_pic < 26) %>%
  mutate(correct = ifelse(post_first_resp_obj == destination, 1, 0)) 
```

```{r echo=FALSE}
a = strsplit(press_twice$other_resp, " ")

same = 0 # not from the same segment 
second = 28
for (i in 2:9) {
  second <- c(second, as.numeric(substring(a[[i]][3], 1, 2)))
    if (as.numeric(substring(a[[i]][3], 1, 2)) < 26) {
      same <- c(same, 1) # from the same segment 
      } else {
        same <- c(same, 0)
      }
  
}

press_twice %>% mutate(from_same_segment = same, second_response = second, end_response = post_first_resp) %>% select(sub, i_pic, end_response, correct, second_response, from_same_segment) %>% gt()
```


4) 

Overall % of trials with more than one response during the route 

```{r}

total_trial = 16 * 6 * 41
target_trial = scan_batch %>% filter(other_resp != "[-999]") %>% select(sub, other_resp, trial)

per = (nrow(target_trial) / total_trial) * 100

print(cat("total number of trials = ", total_trial))
print(cat("number of trials with more than one response during the route = ", nrow(target_trial)))
print(cat("percentage of trials with more than one response = ", per))

scan_batch %>% filter(other_resp != "[-999]") %>% select(sub, other_resp, round, trial) %>% head() %>% gt()

```


5) 

Overall % of trials with more than one response during the route 

*excluding when first response was at image 1 AND there was only one more other response* 

```{r}

multiple = scan_batch %>% filter(other_resp != "[-999]") %>% mutate(correct = ifelse(post_first_resp_obj == destination, 1, 0)) 
v = strsplit(multiple$other_resp, " ")

numOfTimes = 1
for (i in 2:length(v)) {
  n = length(v[[i]]) / 3
  numOfTimes <- c(numOfTimes, n)
}


not_tar = multiple %>% mutate(n_other_res = numOfTimes) %>% filter(i_pic == 1 & n_other_res == 1) 
multiple %>% mutate(n_other_res = numOfTimes) %>% filter(i_pic == 1 & n_other_res == 1) %>% select(sub, i_pic, other_resp, n_other_res, correct) %>% gt()

target = nrow(target_trial) - nrow(not_tar)

per = (target / total_trial) * 100

print(cat("number of target trials (above excluded) = ", target))
print(cat("percentage of trials = ", per))


```


Number of subjects who responded during the same segment 
```{r}
tem2 = multiple %>% mutate(n_other_res = numOfTimes) %>% filter(i_pic == 1 & n_other_res == 1) 

scan_batch %>% mutate(correct = ifelse(post_first_resp_obj == destination, 1, 0)) %>% filter(i_pic < 26 & i_pic != 1 & i_pic != -999 & other_resp == "[-999]") %>% group_by(round) %>% summarise(n=n()) %>% arrange(round) %>% gt()
```




